Determinism, Complexity, and Predictability in Computer Performance

### 2014-03-14 related.tex
a few quick edits

\section{Related Work }\label{sec:related}
{\color{red}[[NOT EDITABLE]]}
Attempting to model time series for prediction is an  old problem which arguably began with Yule in 1927 when he invented autoregression \cite{Yule27}. Since then hundreds if not thousands of prediction strategies have been developed for a wide variety of prediction tasks. The purpose of this paper is \emph{not} to model a time series for prediction but to understand the predictability of a real-valued-scalar time series model free and then to associate the model accuracy with the time series inherent complexity.

Quantifying predictability or sometimes called predicting predictability is also not a new problem and most solutions fall into two categories: model-based error analysis and model-free information analysis.

@@

 Our approach is completely different than this first class as our approach is model free, each of the methods in this class are based off very particular assumptions about the underlying generating system and knowledge of how error will result if those assumptions hold or break. Our approach instead empirically approximates the time series inherent complexity (Kolmogorov-Sinai entropy). Quantifying predictability through entropy/redundancy is not a new idea, but past methods (e.g.,\cite{Shannon1951, mantegna1994linguistic}) have hinged on knowledge of the  \emph{generating partitions}.

>>>>

\section{Related Work }\label{sec:related}
{\color{red}[[NOT EDITABLE]]}
Attempting to model time series for prediction is an old problem which arguably began with Yule in 1927 when he invented autoregression \cite{Yule27}. Since then hundreds if not thousands of prediction strategies have been developed for a wide variety of prediction tasks. The purpose of this paper is \emph{not} to model a time series for prediction but to understand the predictability of a real-valued-scalar time series model free and then to associate the prediction accuracy with the time series inherent complexity.

Quantifying predictability, or what is sometimes called predicting predictability, is also not a new problem and most solutions fall into two categories: model-based error analysis and model-free information analysis.

@@

 Our approach is completely different than this first class as it is model free. Each of the methods in the first class are based off very particular assumptions about the underlying generating system and knowledge of how error will result if those assumptions hold or break. Our approach instead empirically approximates the time series inherent complexity (Kolmogorov-Sinai entropy). Quantifying predictability through entropy/redundancy is not a new idea, but past methods (e.g.,\cite{Shannon1951, mantegna1994linguistic}) have hinged on knowledge of the \emph{generating partition} of the generating system.
